Exposure Consequences - Statistics and Figures

### 2018-05-07 ManuscriptMaterials.Rmd
added online localization to figure

---
title: "Exposure Consequences - Statistics and Figures"
output:
  pdf_document:
    number_sections: yes
    toc: true
    toc_depth: 2
  html_notebook:
    number_sections: yes
    toc: true
    toc_depth: 2
---

@@

```{r fig3_localization, fig.width=7.5, fig.height=4}
plotLocalization()
```

>>>>

---
title: "Exposure Consequences - Statistics and Figures"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
---

@@

```{r fig3_localization, fig.width=7.5, fig.height=2.5}
plotLocalization(classicOnline=TRUE)
```
